The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-14 paper/ms.tex
soem typos corrected

Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
fraction as a function of the rotational velocity. The curves for the
central source distribution stay flat, while for the homogeneous case
there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
the models with low optical depth. For instance, in models with
$\tau_{\rm H}=10^5$, the static escape fraction is $0.26$ and increases
to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
all the values for the escape fraction.

In the right panel of Figure \ref{fig:efvsv} we put these results in the context of
the analytic solution for the infinite slab \citep{Neufeld90}. In
Neufeld's set-up the analytic solution depends uniquely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in the right panel of Figure
\ref{fig:efvsv} show the results for the different rotational
velocities. First of all we note that the escape fraction does not
increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
that is explained since there is a transition from a opaque to an extremely opaque medium
which affect affects how \ly photons escape from the medium: single flight 
vs. single excursion. {\bf Que quiere decir eso de single flight y
  single excursion, porque explica eso la fraccion de escape?}

@@

Furthermore, taking into account all the models that do not event present hints for
a triple peaked emission it would seem that the rotational velocity
and optical depth must balance each other in order to show this feature
feature. Namely, if the rotational velocity is close to half the HFWM
of the line, the triple peaks are more likely to occur. This is the
same threshold that in the case of centered emission marks the
difference between double and single peaked lines.

>>>>

Left panel of Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
fraction as a function of the rotational velocity. The curves for the
central source distribution stay flat, while for the homogeneous case
there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
the models with low optical depth. For instance, in models with
$\tau_{\rm H}=10^5$, the static escape fraction is $0.26$ and increases
to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
all the values for the escape fraction.

In the right panel of Figure \ref{fig:efvsv} we put these results in the context of
the analytic solution for the infinite slab \citep{Neufeld90}. In
Neufeld's set-up the analytic solution depends uniquely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in the right panel of Figure
\ref{fig:efvsv} show the results for the different rotational
velocities. First of all we note that the escape fraction does not
increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
that is explained since there is a transition from an opaque to an extremely opaque medium
which affects how the \ly photons escape from the medium: single flight 
vs. single excursion. {\bf Que quiere decir eso de single flight y
  single excursion, porque explica eso la fraccion de escape?}

@@

Furthermore, taking into account all the models that do not event present hints for
a triple peaked emission it would seem that the rotational velocity
and optical depth must balance each other in order to show this feature
feature. Namely, if the rotational velocity is close to half the FWHM
of the line, the triple peaks are more likely to occur. This is the
same threshold that in the case of centered emission marks the
difference between double and single peaked lines.
